---
title: "Assignment1 Part1 - Team 21"
author: "Matteo Bruscagnin - 834600"
date: "11/7/2021"
output: 
  html_document:
    toc: TRUE
  pdf_document:
    toc: TRUE
---

All solutions are made only by Matteo Bruscagnin.

# Exercise 1

A fair coin is continually flipped. What is the probability that the first four flips are\

(a) *H, H, H, H*?\
    Because every flip is indipendent, and every flip of the fair coin have probability $P(H) = \frac{1}{2}$ the probability of four head is $\frac{1}{2}*\frac{1}{2}*\frac{1}{2}*\frac{1}{2} = \frac{1}{16}$ then $P (HHHH) = p^{4}$\

```{r}
p = 0.5
flips = 4
HHHH = p^flips
HHHH
```

(b) *T, H, H, H*?\
    As we have seen in the previous answer, the probability of every flip is $0.5$ so the probability of one tail and three head will be the same or $P (HHH) * P (T) ==> P (HHH) * (1-p)$ then $P (THHH) = p^{3}(1-p)$\

```{r}
head_flips = flips - 1
HHH = p^head_flips
T = 1-p
THHH = HHH*T
THHH
```

(c) What is the probability that the pattern *T, H, H, H* occurs before the pattern *H, H, H, H*?\
    If in the first four flips we have four heads then the probability is $p4$ as we seen before, so we have to find the probability that in the first 4 flips we not have the pattern HHHH: $P (THHH occurs before HHHH) = 1-p^{4}$.

```{r}
T4Hbefore4H = 1-HHHH
T4Hbefore4H
```

# Exercise 2

Suppose $X$ has a binomial distribution with parameters 6 and $\frac{1}{2}$. Show that $X = 3$ is the most likely outcome.\
Is simple to visualize that with an histogram, e.g. with 3000 observations.

```{r}
observations = 3000
trials = 6
probab = 0.5
x = rbinom(observations, trials, probab)
# rbinom is the function for the random generation for the binomial distribution
hist(x)
```

# Exercise 3

# Exercise 4

# Exercise 5

An urn contains 5 red, 6 blue, and 8 green balls. If a set of 3 balls is randomly selected, what is the probability that each of the balls will be:

```{r}
red = 5
blue = 6
green = 8
n = red + blue + green
k = 3

mutually_exlusive_options <- function(color1, color2, color3, k){
  choose(color1,k) + choose(color2,k) + choose(color3,k)
}
```

*choose(n,k) is the binomial coefficient* $\frac{n!}{k!(n-k)!}$ expressible in form of $\frac{factorial(n)}{(factorial(k) * factorial(n-k))}$

```{r}
same_color <- function(m_e_o, n, k){
  m_e_o / choose(n,k)
}
```

## Without replacement:

### (a) of the same color?

```{r}
same_color(mutually_exlusive_options(red,blue,green,k), n, k)
```

### b) of different colors?

```{r}
(red * blue * green) / choose(n,k)
```

## With replacement:

### (a) of the same color?

```{r}
(red^k+blue^k+green^k) / n^k
```

### b) of different colors?

```{r}
((red*blue*green)*factorial(k)) / n^k
```

# Exercise 6

If there are 12 strangers in a room, what is the probability that no two of them celebrate their birthday in the same month?

```{r}
strangers = 12
tot_months = 12
```

We have $S$ = {x~1~, x~2~, ..., x~12~} with $x$~i~ = {1..12} the outcome space, composed by the months of birth of every stranger.

The dimension of $S$ is: $|S|$ = $12^{12}$

```{r}
outcome_space = tot_months^strangers
options(scipen=1)
# the instruction option(scipen = n) format the numbers from scientific notation
# (scipen = 0) to fixed notation
options(scipen = 999) 
outcome_space
```

We call $A$ the set of all the possible probability of no two strangers have the same month of birth: $|A| = 12!$

The first stranger have birth on every month so the probability that no two strangers have the same month of birth is $P = \frac{12}{12}$;the second one can have any birth month but that of the first stranger: $\frac{11}{12}$, and so on: $\frac{12}{12} * \frac{11}{12} * ... * \frac{1}{12} = 12!/12^{12}$

```{r}
no_birth_same_month = factorial(tot_months) / outcome_space
options(scipen = 1)
no_birth_same_month
```
